Identifying Microlenses in Large, Non-Uniformly Sampled Surveys: The Case of the Palomar Transient Factory

### 2012-08-07 text/ptf_microlensing_paper.tex

\documentclass[12pt,preprint]{aastex}
\newcounter{address}
\setcounter{address}{1}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{subfigure}
\usepackage{natbib}

\newcommand{\apwsim}{\raisebox{0.2ex}{\scriptsize$\sim$\normalsize}}

@@

\title{Title Placeholder}
\author{
  Adrian~M.~Price-Whelan\altaffilmark{\ref{col}}, Marcel~Ag\"ueros\altaffilmark{\ref{col}}, Amanda Fournier\altaffilmark{\ref{ucsb}}, Eran Ofek\altaffilmark{\ref{weiz}}, Rachel Street\altaffilmark{\ref{lcogt}}
}

\altaffiltext{\theaddress}{\stepcounter{address}\label{col} Department of Astronomy, Columbia University, 550 W 120th St., New York, NY 10027, USA}
\altaffiltext{\theaddress}{\stepcounter{address}\label{ucsb} Department of Physics, Broida Hall, University of California, Santa Barbara, CA 93106, USA}
\altaffiltext{\theaddress}{\stepcounter{address}\label{weiz} Benoziyo Center for Astrophysics, Weizmann Institute of Science, 76100 Rehovot, Israel}
\altaffiltext{\theaddress}{\stepcounter{address}\label{lcogt} Las Cumbres Observatory Global Telescope Network, Inc., 6740 Cortona Dr.\ Suite 102, Santa Barbara, CA 93117, USA}

@@

\section{PTF Observations and Data}
[TODO: Marcel]

@@

>>>>

%\documentclass{emulateapj}
\documentclass[12pt,preprint]{aastex}
\newcounter{address}
\setcounter{address}{1}
\usepackage{lscape, longtable}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{subfigure}
\usepackage{natbib}
\newcommand{\Msun}{\ifmmode {M_{\odot}}\else${M_{\odot}}$\fi}
\newcommand{\Rsun}{\ifmmode {R_{\odot}}\else${R_{\odot}}$\fi}
\newcommand{\lapprox }{{\lower0.8ex\hbox{$\buildrel <\over\sim$}}}
\newcommand{\gapprox }{{\lower0.8ex\hbox{$\buildrel >\over\sim$}}}
\def\amin{\ifmmode^{\prime}\else$^{\prime}$\fi}
\def\asec{\ifmmode^{\prime\prime}\else$^{\prime\prime}$\fi}
\newcommand{\apwsim}{\raisebox{0.2ex}{\scriptsize$\sim$\normalsize}}

\slugcomment{DRAFT \today}
\shorttitle{Microlensing \& PTF}
\shortauthors{Price-Whelan et al.}

\bibliographystyle{apj}

@@

\title{Identifying Microlenses in Large, Non-Uniformly Sampled Surveys: The Case
 of the Palomar Transient Factory}
\author{Adrian~M.~Price-Whelan\altaffilmark{\ref{col}}, Marcel~A.~Ag\"ueros\altaffilmark{\ref{col}}, Amanda Fournier\altaffilmark{\ref{ucsb}}, Rachel Street\altaffilmark{\ref{lcogt}}, Eran Ofek\altaffilmark{\ref{weiz},\ref{eins}}, David Levitan\altaffilmark{\ref{calt}}, Joshua S.\ Bloom\altaffilmark{\ref{cal}}, S.\ Bradley Cenko\altaffilmark{\ref{cal}}, Mansi M.\ Kasliwal\altaffilmark{\ref{calt}}, Shrinivas R.\ Kulkarni\altaffilmark{\ref{calt}}, Nicholas~M.~Law\altaffilmark{\ref{to},\ref{dun}}, Peter Nugent\altaffilmark{\ref{lbnl}}, Dovi Poznanski\altaffilmark{\ref{cal},\ref{calt},\ref{eins}}, Robert M.\ Quimby\altaffilmark{\ref{calt}}}

\altaffiltext{\theaddress}{\stepcounter{address}\label{col} Department of Astronomy, Columbia University, 550 W 120th St., New York, NY 10027, USA}
\altaffiltext{\theaddress}{\stepcounter{address}\label{ucsb} Department of Physics, Broida Hall, University of California, Santa Barbara, CA 93106, USA}
\altaffiltext{\theaddress}{\stepcounter{address}\label{lcogt} Las Cumbres Observatory Global Telescope Network, Inc., 6740 Cortona Dr.\ Suite 102, Santa Barbara, CA 93117, USA}
\altaffiltext{\theaddress}{\stepcounter{address}\label{weiz} Benoziyo Center for Astrophysics, Weizmann Institute of Science, 76100 Rehovot, Israel}
\altaffiltext{\theaddress}{\stepcounter{address}\label{calt} Cahill Center for Astrophysics, California Institute of Technology, Pasadena, CA 91125, USA}
\altaffiltext{\theaddress}{\stepcounter{address}\label{cal} Department of Astronomy, University of California, Berkeley, CA  94720, USA}
\altaffiltext{\theaddress}{\stepcounter{address}\label{to} Dunlap Institute for Astronomy and Astrophysics, University of Toronto, 50 St.\ George Street, Toronto M5S 3H4, Ontario, Canada}
\altaffiltext{\theaddress}{\stepcounter{address}\label{lbnl} Computational Cosmology Center, Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, CA 94720, USA}
\altaffiltext{\theaddress}{\stepcounter{address}\label{dun} Dunlap Fellow}
\altaffiltext{\theaddress}{\stepcounter{address}\label{eins} Einstein Fellow}

@@

\section{PTF Observations and Data}
The Palomar Transient Factory is a transient detection system that begins with a wide-field survey camera mounted on the automated 48 inch Oschin Schmidt telescope at Palomar Observatory, CA, uses a real-time data reduction pipeline to identify transients of interest, passes these to a dedicated photometric follow-up telescope, and generates an archive of all detected sources \citep{nick2009,rau2009}.

The PTF camera is the 12K$\times$8K mosaic camera formerly at the Canada-France-Hawaii Telescope. The camera has 11 working chips, 10$^7$ pixels, and a 7.26 deg$^2$ field-of-view \citep{rahmer2008}. Under median seeing conditions (1.1$\arcsec$), observations in Mould $R$ or Sloan Digital Sky Survey (SDSS) $g$ achieve 2.0$\arcsec$ full-width half-maximum images and reach 5$\sigma$ magnitudes of $R \approx 21.0$ and $g \approx 21.3$ mag in a standard 60~s exposure \citep{nick2010}. As of 2012 May, the PTF footprint included $\sim$9800 (2500) deg$^2$ imaged $>$25 ($>$100) times in $R$ and $\sim$2400 (250) deg$^2$ imaged that often in $g$.

[UPDATE NUMBERS FOR FOOTPRINT, INCLUDE FIGURE?]

@@

\acknowledgments
This paper is based on observations obtained with the Samuel Oschin Telescope as part of the Palomar Transient Factory project, a scientific collaboration between the California Institute of Technology, Columbia University, Las Cumbres Observatory, the Lawrence Berkeley National Laboratory, the National Energy Research Scientific Computing Center, the University of Oxford and the Weizmann Institute of Science.

\clearpage
\setlength{\baselineskip}{0.6\baselineskip}
\bibliography{references}
\setlength{\baselineskip}{1.667\baselineskip}
